\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/introduction.tex
Minor
grammarlized introduction

On the other side of the coin, the security of USB has caused serious problems.
The designers of USB protocol did not care much about security issues as they wanted to make an easy-to-use protocol.
There are more than four hundred vulnerabilities referencing USB on CVE list~\cite{website:CVE-list}.
As a result, many attackers exploit these vulnerabilities and the \textit{trust-by-default} characteristics of USB to conduct attacks, which puts the privacy and financial security of USB users in danger~\cite{sok}.

BadUSB is a well-known class of firmware attacks~\cite{badusb}.
These attacks are conducted through modification of the device firmware, which will disguise normal USB devices as other types of devices that are \textit{trust-by-default} by the hosts.
Typical simulated devices include HID (short for human interface devices, including keyboards, mice, etc.) and disks.
Utilizing BadUSB, attackers can pretend themselves as normal users, typing malicious commands to victim computers, downloading and executing malicious scripts, and copying out private data from disks.
Such attacks can easily escape from traditional anti-virus software, since it is hard to distinguish them from normal USB devices.

Despite the advantageous features of BadUSB, there exist several limitations as follows.
(1) Attackers cannot conduct attacks precisely, which decreases the capabilities of BadUSB attacks.
When performing attacks on another host, the attackers can not obtain the current user interface (UI) status which limits them from taking subsequent moves.
For example, it is hard for attackers to locate specific functional UI patterns like buttons and links on victim computers by disguising USB devices as mice.
That explains why typical BadUSB attacks often only stay in command line, using commands to download malicious scripts for execution.
However, these attacks may be intercepted by anti-virus software or firewall due to the usage of host network.
(2) To our best knowledge, existing BadUSB attacks only utilize the features of USB 2.0.
The releasing of USB 3.0 makes USB more powerful, with a higher transmission rate for data and the support towards a larger range of peripherals including DisplayPort, HDMI, PowerDelivery, etc.
BadUSB attacks can become more effective with the help of newly supported features in USB 3.0.
(3) There have emerged multiple efficacious countermeasures after the appearance of BadUSB.
For example, GoodUSB offers a defence method by limiting the functions of USB devices to users' expectations~\cite{tian2015defending}.
It provides a graphical interface for user to describe the functionalities or roles of the USB device and reject any usage beyond the description.
%\shuqing{Can't bypass USBCheckIn.}

In this work, we proposed our approach to address the limitations mentioned above and implemented a multi-mode attack model of USB, named \tool.
\tool extends BadUSB to support the features of USB Type-C.
Since USB Type-C is capable to transfer video stream data, \tool could obtain the information of victim's graphical interface during attacks.
Combining it with simulation of traditional HIDs like keyboards and mice, attackers can perform precise attacks.
We did experiments to verify that \tool could also bypass many countermeasures for BadUSB since they often rely on interaction with the graphical interface.
Moreover, we implemented multiple attacking modes of USB attacks based on our approach to verify its effectiveness, including scripting, remote control, and privacy extraction.
To improve the efficiency and performance of \tool, we designed a filtering algorithm to preprocess the video data before network transmission.
Moreover, we conducted a series of experiments for each attack mode as well as for different types of devices, including smart phones, personal computers, and tablet computers, to validate the usability of \tool.
We also conducted a user study for attacks in sharing power banks, one of the application scenarios of \tool.
During the user study, we obtained plenty of sensitive data through \tool, since users are usually unconscious of the necessity to check the USB devices they plugged in for security purposes.
After the validation of our attack model, we proposed several defence methods as countermeasures, including external hardware authorization, distrust-by-default, etc.
It is worth noting that we designed a method, called isolated UI rendering, to separate the user interface into sensitive and insensitive layers.
Only content on the insensitive layer will be passed to the insecure driver and thus rendered on external display, which protects content on the sensitive layer.
%\shuqing{Case study, evaluation, notable results.}

We summarize our key contributions as follows:
\begin{itemize}
	\item To our best knowledge, this is the first work to utilize new features of USB Type-C.
	The combination of new support with conventional BadUSB makes attacks more precise and effective.
	\item Our approach can bypass many previous countermeasures of BadUSB.
	\item We conducted multiple experiments and a user study to validate the usability and effectiveness of \tool.
	We also proposed several countermeasures for our attack model, which are reasonable and insightful. \fengwei{Add countermeasures, in particular the isolation design.}\shuqing{Isolated UI rendering is added in the last paragraph.}
\end{itemize}

The rest of this paper is structured as follows.
Section~\ref{sec:background} provides the background of USB specification.
Section~\ref{sec:related_work} introduces the existing work of USB security from the aspects of attacking and defence respectively.
In Section~\ref{sec:badusb}, we present the threat model and the overall implementation of \tool in three different modes.
The experiments and user study we conducted are featured in Section~\ref{sec:experiment}.
We presents the possible countermeasures of \tool in Section~\ref{sec:countermeasures}.
The limits and impacts of our approach are discussed in Section~\ref{sec:discussion}, and the conclusion lies in Section~\ref{sec:conclusion}.
%\shuqing{Fill in after the structure is finalized.}

>>>>

On the other side of the coin, the security of USB has caused serious problems.
The designers of the USB protocol did not care much about security issues as they wanted to make an easy-to-use protocol.
There are more than four hundred vulnerabilities referencing USB on CVE list~\cite{website:CVE-list}.
As a result, many attackers exploit these vulnerabilities and the \textit{trust-by-default} characteristics of USB to conduct attacks, which puts the privacy and financial security of USB users in danger~\cite{sok}.

BadUSB is a well-known class of firmware attacks~\cite{badusb}.
These attacks are conducted through modification of the device firmware, which will disguise normal USB devices as other types of devices that are \textit{trust-by-default} by the hosts.
Typical simulated devices include HID (short for human interface devices, including keyboards, mice, etc.) and disks.
Utilizing BadUSB, attackers can pretend themselves as normal users, typing malicious commands to victim computers, downloading and executing malicious scripts, and copying out private data from disks.
Such attacks can easily escape from traditional anti-virus software since it is hard to distinguish them from normal USB devices.

Despite the advantageous features of BadUSB, there exist several limitations as follows.
(1) Attackers cannot conduct attacks precisely, which decreases the capabilities of BadUSB attacks.
When performing attacks on another host, the attackers can not obtain the current user interface (UI) status which limits them from taking subsequent moves.
For example, it is hard for attackers to locate specific functional UI patterns like buttons and links on victim computers by disguising USB devices like mice.
That explains why typical BadUSB attacks often only stay in the command line, using commands to download malicious scripts for execution.
However, these attacks may be intercepted by anti-virus software or firewall due to the usage of the host network.
(2) To our best knowledge, existing BadUSB attacks only utilize the features of USB 2.0.
The release of USB 3.0 makes USB more powerful, with a higher transmission rate for data and the support towards a larger range of peripherals including DisplayPort, HDMI, PowerDelivery, etc.
BadUSB attacks can become more effective with the help of newly supported features in USB 3.0.
(3) There have emerged multiple efficacious countermeasures after the appearance of BadUSB.
For example, GoodUSB offers a defense method by limiting the functions of USB devices to users' expectations~\cite{tian2015defending}.
It provides a graphical interface for users to describe the functionalities or roles of the USB device and reject any usage beyond the description.
%\shuqing{Can't bypass USBCheckIn.}

In this work, we proposed our approach addressing the limitations mentioned above and implemented a multi-mode attack model of USB, named \tool.
\tool extends BadUSB to support the features of USB Type-C.
Since USB Type-C is capable to transfer video stream data, \tool could obtain the information of victim's graphical interface during attacks.
Combining it with the emulation of traditional HIDs like keyboards and mice, attackers can perform precise attacks.
We did experiments to verify that \tool could also bypass many countermeasures for BadUSB since they often rely on interaction with the graphical interface.
Moreover, we implemented multiple attacking modes of USB attacks based on our approach to verify its effectiveness, including scripting, remote control, and privacy extraction.
To improve the efficiency and performance of \tool, we designed a filtering algorithm to preprocess the video data before network transmission.
Moreover, we conducted a series of experiments for each attack mode as well as for different types of devices, including smartphones, personal computers, and tablet computers, to validate the usability of \tool.
We also conducted a user study for attacks in sharing power banks, one of the application scenarios of \tool.
During the user study, we obtained plenty of sensitive data through \tool, since users are usually unconscious of the necessity to check the USB devices they plugged in for security purposes.
After the validation of our attack model, we proposed several defense methods as countermeasures, including external hardware authorization, distrust-by-default, etc.
It is worth noting that we designed a method, called isolated UI rendering, to separate the user interface into sensitive and insensitive layers.
Only content on the insensitive layer will be passed to the insecure driver and thus rendered on the external display, which protects content on the sensitive layer.
%\shuqing{Case study, evaluation, notable results.}

We summarize our key contributions as follows:
\begin{itemize}
	\item To our best knowledge, this is the first work to utilize new features of USB Type-C.
	The combination of new support with conventional BadUSB makes attacks more precise and effective.
	\item Our approach can bypass many previous countermeasures of BadUSB.
	\item We conducted multiple experiments and a user study to validate the usability and effectiveness of \tool.
	We also proposed several countermeasures for our attack model, which are reasonable and insightful. 
	%\fengwei{Add countermeasures, in particular the isolation design.}
	%\shuqing{Isolated UI rendering is added in the last paragraph.}
\end{itemize}

The rest of this paper is structured as follows.
Section~\ref{sec:background} provides the background of USB specification.
Section~\ref{sec:related_work} introduces the existing work of USB security from the aspects of attacking and defense respectively.
In Section~\ref{sec:badusb}, we present the threat model and the overall implementation of \tool in three different modes.
The experiments and user study we conducted are featured in Section~\ref{sec:experiment}.
We present the possible countermeasures of \tool in Section~\ref{sec:countermeasures}.
The limits and impacts of our approach are discussed in Section~\ref{sec:discussion}, and the conclusion lies in Section~\ref{sec:conclusion}.
%\shuqing{Fill in after the structure is finalized.}
